Model for Porous Silicon Structures with a Lateral Gradient

### 2020-10-28 paper.tex
Remove extra space
Start correcting manuscript. Title.

\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

\affil[1]{Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de
  Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\affil[2]{Instituto de Ciencias F\'isica ,Universidad Nacional
  Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, Mexico}
\affil[3]{Centro de Investigaci\'on en Ingenier\'ia y Ciencias
  Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001
  Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  }
\begin{document}

\maketitle

\begin{abstract}
We propose a simple setup which that the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.
\notaV{ABSTRACT :  Surfaces with the gradient in the refractive index 
have attracted attention due to their ability to unpair the relation
 between the shape of the optical lens with its optical response. 
  For enhancing the versatility  of electrochemical gradients and its possible usage in
different kinds of devices and applications, it is
desirable to predesign GRIN structures with spatial 
predictability of porosity and the corresponding etching rate.  
In this work, we propose a simple model for the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous silicon structures with a controlled gradient in their
index of refraction. The characterization of some typical PS samples with 
lateral porosity and thickness gradient (produced using pin Pt electrode) 
with scanning electron microscopy and
ultraviolet-visible-near infrared reflectance spectroscopy was 
found to be in conformity with the properties predicted through 
the proposed model. In addition,
as the results allow us to obtain the complete dependence of
porosity, dielectric function and the corresponding etching rate for each 
current density from some measurements performed on a single or 
a couple of samples, the proposed model can facilitate the designing 
of novel sensing devices based on surfaces with lateral gradient in refractive indices.}
Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}

>>>>

\title{Model for Porous Silicon Structures with a Lateral Gradient}
\author[1]{C. A. Ospina de la Cruz}
\author[2]{V. Agarwal}
\author[3]{W. L. Mochán}

\affil[1]{Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de
  Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\affil[2]{Centro de Investigaci\'on en Ingenier\'ia y Ciencias
  Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001
  Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  }
\affil[3]{Instituto de Ciencias F\'isica ,Universidad Nacional
  Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, Mexico}
\begin{document}

\maketitle
\notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME;
  Probably "Analytical model for  porous silicon structures with 1D
  gradient refractive index)}
\notaL{The calculation is 2D, seems 1D due to the narrow geometry chosen.}
\begin{abstract}
We propose a simple setup which that the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.
\notaV{ABSTRACT :  Surfaces with the gradient in the refractive index
have attracted attention due to their ability to unpair the relation
 between the shape of the optical lens with its optical response.
  For enhancing the versatility  of electrochemical gradients and its possible usage in
different kinds of devices and applications, it is
desirable to predesign GRIN structures with spatial
predictability of porosity and the corresponding etching rate.
In this work, we propose a simple model for the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous silicon structures with a controlled gradient in their
index of refraction. The characterization of some typical PS samples with
lateral porosity and thickness gradient (produced using pin Pt electrode)
with scanning electron microscopy and
ultraviolet-visible-near infrared reflectance spectroscopy was
found to be in conformity with the properties predicted through
the proposed model. In addition,
as the results allow us to obtain the complete dependence of
porosity, dielectric function and the corresponding etching rate for each
current density from some measurements performed on a single or
a couple of samples, the proposed model can facilitate the designing
of novel sensing devices based on surfaces with lateral gradient in refractive indices.}
Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}
